Title of the document here

### 2015-02-06 rmtw/assignment_1/assignment_1.tex
sasda

Write how the questionnaire was distributed. (I.e. facebook pages of all 3 years):::::
Sampling bias is a considerable challenge in research \cite{easterbrook2008selecting} and thus the questionnaire will be distributed to the Facebook page of all three year's.

>>>>

Write how the questionnaire was distributed. (I.e. facebook pages of all 3 years --> Sampling bias is a considerable challenge in research \cite{easterbrook2008selecting} and thus the questionnaire will be distributed to the Facebook page of all three years (and not only 1st years with Java experience, for example).
